maps

### 2022-11-05 code/maps.qmd
Use tm_rgb to map hillshade raster

---
title: "maps"
format: html
editor: visual
---
## Load packages
```{r}
library(sf)
library(tmap)
library(stars)
library(tidyverse)
```

## Map of sample sites for exome capture analysis
### Import data
```{r}
nps_boundary <- st_read("/home/roland/pCloudDrive/MLRG/gis/Coverages/NPS_boundary/yose_kica_sequ_boundaries.shp", stringsAsFactors=F) #read in shapefile like a dataframe using sf package
class(nps_boundary)
str(nps_boundary)
st_crs(nps_boundary) #determine CRS
utm11nCRS <- st_crs(nps_boundary)

# California Color Hillshade (90m) from koordinates.com
hillshade <- read_stars("/home/roland/Downloads/hillshade-90m-GTiff-UTMzone11/california-color-hillshade-90m.tif")
hillshade

@@

### Check if shapefile polygons are valid
```{r}
st_is_valid(nps_boundary) # all 3 are invalid

@@

### Create map
```{r}
tm_shape(hillshade) + 
  tm_raster(style = "cont") + 
  tm_shape(nps_boundary) +
  tm_polygons()

tm_shape(nps_boundary) +
  tm_polygons()

@@

>>>>

---
title: "maps"
format: html
editor: visual
---

## Load packages

```{r}
library(sf)
library(tmap)
library(stars)
library(tidyverse)
```

## Map of sample sites for exome capture analysis

### Import data

```{r}
nps_boundary <- st_read("/home/roland/pCloudDrive/MLRG/gis/Coverages/NPS_boundary/yose_kica_sequ_boundaries.shp", stringsAsFactors=F) #read in shapefile like a dataframe using sf package
class(nps_boundary)
str(nps_boundary)
st_crs(nps_boundary) #determine CRS
#utm11nCRS <- st_crs(nps_boundary)

# California Color Hillshade (90m) from koordinates.com
hillshade <- read_stars("/home/roland/Downloads/hillshade-90m-GTiff-UTMzone11/california-color-hillshade-90m.tif")
hillshade
str_rgb
st_crs(hillshade)

@@

### Check if shapefile polygons are valid

```{r}
st_is_valid(nps_boundary) # all 3 are invalid

@@

### Set projection

```{r}
crs(hillshade) <- crs(nps_boundary)
```

### Crop raster with bounding box

```{r}
# as example
b <- as(extent(6, 6.4, 49.75, 50), 'SpatialPolygons')
crs(b) <- crs(r)
rb <- crop(r, b)
```

### Create map

```{r}
tm_shape(hillshade) + 
  tm_rgb(r = 1, g = 2, b = 3) +
  tm_shape(nps_boundary) + 
  tm_borders(col = "black")

# Need to crop raster to smaller size: https://semba-blog.netlify.app/12/14/2020/manipulate-and-visualize-raster-data-with-leaflet-and-tmap-in-r/#crop-raster

# Might be easier to re-export smaller shape

@@

Add study site points, north arrow, distance bar
